Metrics

### 2023-11-26 src/metrics.Rmd
Add labels and values to plot

```{r}
out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`,
        `PCCC Reconciliation`,
        `PCCC Adjudication`
    ) %>%
    rename(
         All = `PCCC`,
         Agreement = `PCCC Agreement`,
         Reconciliation = `PCCC Reconciliation`,
         Adjudication = `PCCC Adjudication`
    ) %>%
    pivot_longer(
        cols = -Model,
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    mutate(
        Stage = factor(Stage, levels = c(
            "Adjudication",
            "Reconciliation",
            "Agreement",
            "All"
        ))
    ) %>%
    ggplot(aes(x = Stage, y = PCCC)) +
    geom_boxplot(width = 0.4) +
    stat_summary(
        geom = "label",
        fun.y = min,
        aes(label = sprintf("%1.2f", ..y..)),
        position = position_nudge(y = -0.07),
        size = 2.5
    ) +
    stat_summary(
        geom = "label",
        fun.y = max,
        aes(label = sprintf("%1.2f", ..y..)),
        position = position_nudge(y = 0.06),
        size = 2.5
    ) +
    ylim(0, 1) +
    coord_flip() +
    theme_minimal()
```

>>>>

# Calc stage counts
nall <- nrow(df)
nagree <- nrow(df %>% filter(is_agreed == TRUE))
nrecon <- nrow(df %>% filter(is_recon == TRUE))
nadj <- nrow(df %>% filter(is_adj == TRUE))

# Calc stage perc
pagree <- (nagree / nall) * 100
precon <- (nrecon / nall) * 100
padj <- (nadj / nall) * 100

# Create stage with counts
stage_remap <- c(
    "All" = paste0("All\n(n=", nall, ", 100%)"),
    "Agreed" = paste0("Agreed\n(n=", nagree, ", ", round(pagree), "%)"),
    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
)

#

# Prepare boxplot data
pdata <- out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`
    ) %>%
    rename(
         All = `PCCC`,
         Agreed = `PCCC Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    mutate( # re-order stage
        Stage = factor(Stage, levels = c(
            "Agreed",
            "All"
        ))
    ) %>%
    mutate( # rename stages with counts
        Stage = recode(Stage, !!!stage_remap)
    ) %>%
    group_by(Stage) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
    )

# Plot boxplot
pdata %>%
    ggplot(aes(x = Stage, y = PCCC)) +
    geom_boxplot(width = 0.25) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#3d3d3d",
        size = 2,
        position = position_nudge(y = -0.06, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#3d3d3d",
        size = 2,
        position = position_nudge(y = 0.065, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#3d3d3d",
        size = 2,
        position = position_nudge(y = -0.065, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    labs(
        x = element_blank(),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.2, 0.8) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5))
    )
```
